---
title: "Social and Cultural Dynamics Exam ABM"
author: "Rebecca and Katrine"
output: 
  md_document:
    variant: gfm
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#INTRODUCTION 
This script computes an Agent-Based Model in which a group of agents has to solve a task, either in groups where they have the same level of ability of mixed levels. 

The model needs 4 fixed parameter: 
- N_agents = number of agents 
- rounds = number of rounds 
- teaching = the effect of teaching varying from 0-0.4
When you run the model it outputs a dataframe containing the score for each agent on every round. 
From this dataframe you can plot how the agents performed given the fixed parameters. 

The model uses 4 predefined functions: 
- simulation() 
- getScore()
- runTask()
Each of these functions are defined below in the script along with explanations of what they do.

#SETUP
```{r Setup}
library(pacman)
p_load(ggplot2, tidyverse, patchwork, reshape)

# to get the same result across runs.
set.seed(177)
```

#MAKING GROUPS
```{r Group-making}

# We define the error rate as four different ones. 
group_n <- c(1, 2, 3, 4)
newbie <- round(c(runif(4, 0.10, 0.20)), 2)
novice <- round(c(runif(4, 0.20, 0.30)), 2)
master <- round(c(runif(4, 0.30, 0.40)), 2)
expert <- round(c(runif(4, 0.40, 0.50)), 2)

# combine it into a dataframe for mixed groups
df_mixed <- data.frame(group_n, newbie, novice, master, expert)

# We define a group_n for the similar groups with the numbers from 5-8
group_n <- c(5, 6, 7, 8)

# We make a df for same level groups
df_similar <- as.data.frame(rbind(newbie, novice, master, expert))
df_similar$group_n <- group_n
df_similar <- melt(df_similar, id.vars = c("group_n"))
df_similar$id <- seq.int(nrow(df_similar))

# We make the agent_type column
agent_type <- rep(c("newbie", "novice", "master", "expert"), 4)
# make uniform/similar groups
df_similar$variable <- agent_type
df_similar <- rename(df_similar, c("variable" = "agent_type"))

# Specify id.vars: the agent_types to keep but not split apart on
df_mixed <- melt(df_mixed, id.vars=c("group_n"))
df_mixed <- rename(df_mixed, c("variable" = "agent_type"))
df_mixed$id <- seq.int(from = 17, to = 32)
#reorder by column index
df_mixed <- df_mixed[c(4,1,3,2)]
```


#SIMULATION FUNCTION - simulation()

How the function works: 
- The simulation function takes the four inputs described above. 

- Generate a dataframe containing 8 columns: 
1) id. 2) group_n. 3) agent_type. 4) solving_rate. 5) round. 6) score of the agent. 7) whether the agent did teach/learn. 8) The teaching effect for that simulation.

- Generate a matrix storing the guesses (combination of digits) of each agent in each round. The matrix has 3 dimensions (agent, digits, round). That is, for each round we have a 2D matrix containing N rows (one for each agent) and 50 columns (one for each digit). To index the guess of agent 3 on round 5: guesses[3, ,5].  
    
- Run loop to set op the values of the first round. For each agent, the loop does three things: 1) give the agent a first guess, by sampling 15 digits of 0 ) get the score of that guess (using the getScore() function) and add the score to the df, and 3) add the guess of the each agent to the guesses list of the first round. 

- Run learning. For each round, the loop does 3 things:
     - Run task and update the df and guesses matrix.
     - Calculate the mean score for the agent types and groups.
     - Return the dataframe (df) after running all rounds. 

```{r}
simulation <- function(N_agents,rounds, teaching){
  
  #Create df for round number, score etc
  df <-  data.frame(id = rep(1:N_agents, rounds), round = rep(1:rounds, each = N_agents), score = NA, Teaching_or_learning = NA, teaching_effect = teaching)
  df_groups <- rbind(df_similar, df_mixed)
  df <- cbind(df, df_groups)
  df <- df[c(1,6, 7,8, 2,3,4, 5)]
  df <- rename(df, c("value" = "solving_rate"))

  
  # 3-Dimensional array to keep track of the agent's guesses - Dimensions [agent, digits, round]
  guesses = array(0,c(N_agents,50,rounds))   

  #Setup values for first round 
  for(agent in 1:N_agents){
    firstGuess <- round(runif(50, 0, 0) ,0) 
    guesses[agent,,1] <- firstGuess
    df$score[df$round==1 & df$id == agent] <- getScore(firstGuess)
  }
 ### Set up other columns in df here
  # We want a column specifying the group type
  df$group_type <- ifelse(df$group_n < 5, "mixed", "uniform")
  
  # We want a mean for each group type 
  df$mean_group[df$round==1 & df$group_n < 5] <- mean(df$score[df$round==1 & df$group_n<5])
  df$mean_group[df$round==1 & df$group_n > 4] <- mean(df$score[df$round==1 & df$group_n>4])
  
  # We want a mean for each agent_type
   df$mean_agent_type[df$round==1 & df$agent_type == "newbie" & df$group_type ==  "uniform"] <- mean(df$score[df$round==1 & df$agent_type == "newbie"  & df$group_type ==  "uniform"])
   
  df$mean_agent_type[df$round==1 & df$agent_type == "novice" & df$group_type ==  "uniform"] <- mean(df$score[df$round==1 & df$agent_type == "novice" & df$group_type ==  "uniform"])
  
  df$mean_agent_type[df$round==1 & df$agent_type == "master" & df$group_type ==  "uniform"] <- mean(df$score[df$round==1 & df$agent_type == "master" & df$group_type ==  "uniform"])
  
  df$mean_agent_type[df$round==1 & df$agent_type == "expert" & df$group_type ==  "uniform"] <- mean(df$score[df$round==1 & df$agent_type == "expert" & df$group_type ==  "uniform"])
  
  df$mean_agent_type[df$round==1 & df$agent_type == "newbie" & df$group_type ==  "mixed"] <- mean(df$score[df$round==1 & df$agent_type == "newbie"  & df$group_type ==  "mixed"])
  
  df$mean_agent_type[df$round==1 & 
                     df$agent_type == "novice" & 
                     df$group_type ==  "mixed"] <- 
    mean(df$score[df$round==1 & df$agent_type == "novice" & df$group_type ==  "mixed"])
  
  df$mean_agent_type[df$round==1 & df$agent_type == "master" & df$group_type ==  "mixed"] <-mean(df$score[df$round==1 & df$agent_type == "master" & df$group_type ==  "mixed"])
  
  df$mean_agent_type[df$round==1 & df$agent_type == "expert" & df$group_type ==  "mixed"] <- mean(df$score[df$round==1 & df$agent_type == "expert" & df$group_type ==  "mixed"])
  
  #Run learning
  for(round in 2:rounds){

    task <- runTask(df, guesses, round, N_agents, teaching)
    df <- task$df
    guesses <- task$guesses

     # We want a mean for each group type 
  df$mean_group[df$round==round & df$group_n < 5] <- mean(df$score[df$round==round & df$group_n<5])
  df$mean_group[df$round==round & df$group_n > 4] <- mean(df$score[df$round==round & df$group_n>4])
  
  # We want a mean for each agent_type
  df$mean_agent_type[df$round==round & 
                     df$agent_type == "newbie" & df$group_type ==  "uniform"] <- 
    mean(df$score[df$round==round & 
                    df$agent_type == "newbie" & df$group_type ==  "uniform"])
  df$mean_agent_type[df$round==round 
                   & df$agent_type == "novice" & df$group_type ==  "uniform"] <- 
    mean(df$score[df$round==round & 
                    df$agent_type == "novice" & df$group_type ==  "uniform"])
  df$mean_agent_type[df$round==round & 
                     df$agent_type == "master" & df$group_type ==  "uniform"] <- 
    mean(df$score[df$round==round & 
                    df$agent_type == "master" & df$group_type ==  "uniform"])
  df$mean_agent_type[df$round==round & 
                     df$agent_type == "expert" & df$group_type ==  "uniform"] <- 
    mean(df$score[df$round==round & 
                    df$agent_type == "expert" & df$group_type ==  "uniform"])
   df$mean_agent_type[df$round==round & 
                      df$agent_type == "newbie" & df$group_type ==  "mixed"] <- 
    mean(df$score[df$round==round & 
                    df$agent_type == "newbie"  & df$group_type ==  "mixed"])
  df$mean_agent_type[df$round==round & df$agent_type == "novice" & df$group_type ==  "mixed"] <- 
    mean(df$score[df$round==round & df$agent_type == "novice" & df$group_type ==  "mixed"])
  df$mean_agent_type[df$round==round & df$agent_type == "master" & df$group_type ==  "mixed"] <- 
    mean(df$score[df$round==round & df$agent_type == "master" & df$group_type ==  "mixed"])
  df$mean_agent_type[df$round==round & df$agent_type == "expert" & df$group_type ==  "mixed"] <- 
    mean(df$score[df$round==round & df$agent_type == "expert" & df$group_type ==  "mixed"])
  
  # We want a mean endscore for all hetero and all homo groups
  df$mean_endscore[df$group_n < 5 & df$round == round] <- 
    mean(df$score[df$group_n<5 & df$round == rounds])
  df$mean_endscore[df$group_n > 4 & df$round == round] <- 
    mean(df$score[df$group_n>4 & df$round == rounds])
  }
  
  return(df)
}

```

#Task FUNCTION - runTask() 

How the function works: 
- It takes the df, guesses, round and N_agents as input 
- Loop through all groups
- Loop through all the agents in each group
- Create a new df containing only the values from the previous round. 
- Extract the previous score of that agent
- Extract the previous guess from that agent 
- Find the best scoring agent
- For mixed groups:
     - If yourself, you gain a higher probability of matching the string, but don't get to change a digit
- For uniform groups:
     - If yourself, you can change a digit in your string
- If another you take his/her guess and change one incorrect number
- If all of you have the best guess, all change one incorrect number
- Compute the score of the new guess 
- Add the new score to the df 
- Add the new guess to the guesses matrix 
- Return the updated df and guesses matrix 

```{r}

#Function to run tasks
runTask <- function(df, guesses, round, N_agents, teaching){
  for (group in 1:length(unique(df$group_n))){
    df_group <- subset(df, group_n == group)
    for (i in 1:length(unique(df_group$id))){ # 
      prevRound <- df_group[df_group$round==round-1,]
      prevScore <- prevRound$score[i] 
      prevGuess <- guesses[prevRound$id[i],,round-1]
      # Draw random number between 0-9 for each group member only for i = 1
      if(i == 1) {
          draw_uncertainty <- c(sample(0:9,4, replace=TRUE))
          # Save teaching/learning as no if the number is 9 for each agent 
          prevRound$Teaching_or_learning[i] <- ifelse(draw_uncertainty[1] == 9, 
                                                      "No", "Yes")
          prevRound$Teaching_or_learning[i+1] <- ifelse(draw_uncertainty[2] == 9, 
                                                      "No", "Yes")
          prevRound$Teaching_or_learning[i+2] <- ifelse(draw_uncertainty[3] == 9, 
                                                      "No", "Yes")
          prevRound$Teaching_or_learning[i+3] <- ifelse(draw_uncertainty[4] == 9, 
                                                      "No", "Yes")
          # Save it to the overall df
          df$Teaching_or_learning[df$round == round-1 & 
                 df$id == prevRound$id[i] & 
                 df$group_n == group] <- prevRound$Teaching_or_learning[i]
          
          df$Teaching_or_learning[df$round == round-1 & 
                 df$id == prevRound$id[i+1] & 
                 df$group_n == group] <- prevRound$Teaching_or_learning[i+1]
          
          df$Teaching_or_learning[df$round == round-1 & 
                 df$id == prevRound$id[i+2] & 
                 df$group_n == group] <- prevRound$Teaching_or_learning[i+2]
          df$Teaching_or_learning[df$round == round-1 & 
                 df$id == prevRound$id[i+3] & 
                 df$group_n == group] <- prevRound$Teaching_or_learning[i+3]
          
          #Save it to the df_group
          df_group$Teaching_or_learning[df_group$round == round-1 & 
                 df_group$id == prevRound$id[i]] <- prevRound$Teaching_or_learning[i]
          
          df_group$Teaching_or_learning[df_group$round == round-1 & 
                 df_group$id == prevRound$id[i+1]] <- prevRound$Teaching_or_learning[i+1]
          
          df_group$Teaching_or_learning[df_group$round == round-1 & 
                 df_group$id == prevRound$id[i+2]] <- prevRound$Teaching_or_learning[i+2]
          df_group$Teaching_or_learning[df_group$round == round-1 & 
                 df_group$id == prevRound$id[i+3]] <- prevRound$Teaching_or_learning[i+3]
            
      }
      # check whether you should cooperate or work individually
      if (prevRound$Teaching_or_learning[i] == "No"){ # 10% of times agents do individual learning
            # Use your own previous guess
            newGuess <- prevGuess 
           
            # Change numbers that is not matching with target string
            stop <- 0
            k <- 1
            while (stop == 0){
              if (newGuess[k] != target_string[k]){
                Diff <- target_string - newGuess
                  if (Diff[k] > 0){
                  prevGuess_k <- newGuess[k] + rbinom(1, Diff[k], prevRound$solving_rate[i])
                  }
                  else { 
                    sqrt((Diff[k])^2)
                    prevGuess_k <- newGuess[k] - rbinom(1, Diff[k], prevRound$solving_rate[i])
                  }
                # They slowly get closer to the target solving_rate for each round. 
                newGuess[k] <- prevGuess_k
                stop <- 1
                } # changes a number in the string --> stops --> next round 
              else{ # If guess[k] = target[k] then it takes k + 1
                k = k+1 # Next number in the guess
              }
              }
          }
      else{ # The other 90% of the time they will cooperate

          #The code finds the guess of the best members (highest score) in previous round
            # We need to use the highest score of member you have a "yes" in teaching or learning
        # A max score df for everyone cooperating or not to use for the next if statement
            all_score <- subset(prevRound, prevRound$score == max(prevRound$score))
            maxScore_df <- as.data.frame(
              subset(prevRound, Teaching_or_learning == "Yes"))
            maxScore_df <- subset(maxScore_df, maxScore_df$score == max(maxScore_df$score))
          
            # Takes out one row of max scores in case of multiple
            maxScore <- maxScore_df[sample(nrow(maxScore_df), 1), ]
   
          # if you have the highest score last time and if not all members have it and you are a mixed group
            if(prevRound$group_n[i] <= 4 &
               nrow(all_score) < 4 & 
               maxScore$score == prevRound$score[i]){
              newGuess <- prevGuess 
          # Means you wait till everyone has the same as you. 
          ## The effect of teaching
          # We will overwrite the solving_rate (error rate) for this agent like +0.01
              if (prevRound$solving_rate[i] + teaching < 1){
              for (error_round in round:rounds) {
                df$solving_rate[df$id == prevRound$id[i] &
                           df$round == error_round &
                           df$group_n == group] <- prevRound$solving_rate[i] + teaching
              }
              }
              else {
                prevRound$solving_rate[i] == 1
                }
          }
          #If you did not score highest you will use the highest scoring guess
            else if (maxScore$score > prevRound$score[i]){
          #Use the guess of the best scoring agent 
              newGuess <- guesses[maxScore$id,,round-1] #Index the guess of the best agent
            }
            # If you did score the max then you will optimize by changing a number in your guess
            # Change numbers that is not matching with target string
            else {
              newGuess <- prevGuess
              stop <- 0
              k <- 1
              while (stop == 0){
                if (newGuess[k] != target_string[k]){
                  Diff <- target_string - newGuess
                  if (Diff[k] > 0){
                  prevGuess_k <- newGuess[k] + rbinom(1, Diff[k], prevRound$solving_rate[i])
                  }
                  else { 
                    sqrt((Diff[k])^2)
                    prevGuess_k <- newGuess[k] - rbinom(1, Diff[k], prevRound$solving_rate[i])
                  }
                 # They slowly get closer to the target solving_rate for each round. 
                  newGuess[k] <- prevGuess_k
                  stop <- 1
                  } # changes a number in the string --> stops --> next round 
                else{ # If guess[k] = target[k] then it takes k + 1
                  k = k+1 # Next number in the guess
              }
              }
          }
          }
          # We save a score for the new guess
          score <- getScore(newGuess)
          #We save the newguess into the guesses matrix 
          guesses[prevRound$id[i],,round] <- newGuess # newGuess into the guesses matrix
          # Save it to the overall df
          df$score[df$round == round & 
                 df$id == prevRound$id[i] & 
                 df$group_n == group] <- score
        }
    }
  output <- list(df=df, guesses=guesses)
  return(output)
}

```


#GET SCORE FUNCTION - getScore()

How the function works: 
- It takes a guess (list of 50 digits) as input
- Set the score to 0 
- Loop through each of the 50 digits: 
  - If the digit is equal to the same digit in the target string, then add 1 to the score. 
  - If not, do nothing, and continue with the next digit. 
- Return the score. 

```{r Get score}
#Function to calculate score 
getScore <- function(guess){
  score = 0
  for(i in 1:50){
    if(guess[i] == target_string[i]){
      score = score+1
      i = i+1
    }
  }
  return(score)
}
```


#RUN SIMULATION 

- First, we setup the task. The task is defined as a string of 50 digtis between 0 and 9. The agents have to figure out the correct combination of digits. On every round, they produce one guess.  

- Second, we run a simulation using the simulation() function. The simulation function takes 4 inputs: N_agents = number of agents, rounds = number of rounds, effect of teaching. The function outputs a dataframe, containing the performance of each agent on each round.

```{r Run simulation}
#Setup task 
target_string = c(sample(0:9,50, replace=TRUE))

# Run simulation
Class_000 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.00 # Can be changed 
)

# Run simulation
Class_001 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.001 # Can be changed 
)

# Run simulation
Class_005 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.005 # Can be changed 
)

# Run simulation
Class_01 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.01 # Can be changed 
)

# Run simulation
Class_015 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.015 # Can be changed 
)

# Run simulation
Class_02 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.020 # Can be changed 
)

# Run simulation
Class_025 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.025 # Can be changed 
)

# Run simulation
Class_03 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.03 # Can be changed 
)

# Run simulation
Class_035 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.035 # Can be changed 
)

# Run simulation
Class_04 <- simulation(
  N_agents <- 32,
  rounds <- 70, # Can be changed
  teaching <- 0.04 # Can be changed 
)
```

#PLOT RESULTS 
```{r}

#Combine data 
all_data <- rbind(Class_000, Class_001, Class_005, Class_01, Class_015, Class_02, Class_025, Class_03, Class_035, Class_04 ) 
all_data$teaching_effect <- as.factor(all_data$teaching_effect)

####### DESCRIPTIVE STATS #######
# We filter out the data with teaching effect == 0.03
Class <- filter(all_data, teaching_effect == 0.03)
# We filter out the last round
C <- filter (Class, round == 70)
# We calculate mean for last round in the two groups
mean(C$score[C$group_type == "uniform"])
mean(C$score[C$group_type == "mixed"])
sd(C$score[C$group_type == "mixed"])
sd(C$score[C$group_type == "uniform"])

# figure 3
mix <- filter(Class, group_type == "mixed")
uni <- filter(Class, group_type == "uniform")
model_uni <- lm(score ~ round, data = uni)
model_mix <- lm(score ~ round, data = mix)
# betas and sd
summary(model_uni) 
summary(model_mix) 
model_uni <- summary(model_uni) 
model_uni$coefficients[1, 2] * sqrt(70)
model_mix <- summary(model_mix)
model_mix$coefficients[1, 2] * sqrt(70)


# We find the regression for the last plot / figure 5
prob_score_exp <- Class_03 %>% filter(group_type == "mixed")
model_exp <- lm(solving_rate ~ 0 + round, data = prob_score_exp[prob_score_exp$agent_type == "expert",])
summary(model_exp)
model_mas <- lm(solving_rate ~ 0 + round, data = prob_score_exp[prob_score_exp$agent_type == "master",])
summary(model_mas)
model_nov <- lm(solving_rate ~ 0 + round, data = prob_score_exp[prob_score_exp$agent_type == "novice",])
summary(model_nov)
model_new <- lm(solving_rate ~ 0 + round, data = prob_score_exp[prob_score_exp$agent_type == "newbie",])
summary(model_new)

# extract SD: Sd = se * sqrt(simulationsN) for last plot
model_exp <- summary(model_exp) 
model_exp$coefficients[, 2] * sqrt(70)

model_mas <- summary(model_mas)
model_mas$coefficients[, 2] * sqrt(70)

model_nov <- summary(model_nov)
model_nov$coefficients[, 2] * sqrt(70)

model_new <- summary(model_new)
model_new$coefficients[, 2] * sqrt(70)

####### PLOTS FOR RESULT SECTION #######

# We want to see how the effect of teaching changes the endscore
ggplot(all_data[all_data$round == 70,], aes(x = teaching_effect, y = mean_endscore, fill = group_type)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(x=teaching_effect, ymin=mean_endscore-sd(mean_endscore), ymax=mean_endscore+sd(mean_endscore)), position = "dodge") +
  labs(title = "Effect of teaching on final score") +
  xlab ("teaching effect") + ylab ("mean score") +
  labs(fill = "Group type") +
  theme(text=element_text(size=30,  family="serif")) + 
  scale_fill_manual(values = c( "forestgreen", "#66B2FF"))


# seperate for each agent type
experts <- ggplot(all_data[all_data$agent_type == "expert" & all_data$round == 70,], aes(x = teaching_effect, y = mean_agent_type, fill = group_type)) + geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(x=teaching_effect, ymin=mean_agent_type-sd(mean_agent_type), ymax=mean_agent_type+sd(mean_agent_type)), position = "dodge") +
  labs(title = "Effect of teaching on the mean score for experts") + 
  xlab ("teaching effect") + ylab ("mean score") + 
  theme(text=element_text(size=16,  family="serif")) + 
  scale_fill_manual(values = c( "forestgreen", "#66B2FF")) 

newbies <- ggplot(all_data[all_data$agent_type == "newbie"& all_data$round == 70,], aes(x = teaching_effect, y = mean_agent_type, fill = group_type)) + geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(x=teaching_effect, ymin=mean_agent_type-sd(mean_agent_type), ymax=mean_agent_type+sd(mean_agent_type)), position = "dodge") +
  labs(title = "Effect of teaching on the mean score for newbies") + 
  xlab ("teaching effect") + ylab ("mean score") +
  theme(text=element_text(size=16,  family="serif")) + 
  scale_fill_manual(values = c( "forestgreen", "#66B2FF"))

novices <- ggplot(all_data[all_data$agent_type == "novice" & all_data$round == 70,], aes(x = teaching_effect, y = mean_agent_type, fill = group_type)) + geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(x=teaching_effect, ymin=mean_agent_type-sd(mean_agent_type), ymax=mean_agent_type+sd(mean_agent_type)), position = "dodge") +
  labs(title = "Effect of teaching on the mean score for novices") + 
  xlab ("teaching effect") + ylab ("mean score") +
  theme(text=element_text(size=16,  family="serif")) + 
  scale_fill_manual(values = c( "forestgreen", "#66B2FF"))

masters <- ggplot(all_data[all_data$agent_type == "master" & all_data$round == 70,], aes(x = teaching_effect, y = mean_agent_type, fill = group_type)) + geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar(aes(x=teaching_effect, ymin=mean_agent_type-sd(mean_agent_type), ymax=mean_agent_type+sd(mean_agent_type)), position = "dodge") +
  labs(title = "Effect of teaching on the mean score for masters") + 
  xlab ("teaching effect") + ylab ("mean score") +
  theme(text=element_text(size=16,  family="serif")) + 
  scale_fill_manual(values = c( "forestgreen", "#66B2FF"))

experts + theme(legend.position = "none") + masters +  theme(legend.position = "none") + novices + theme(legend.position = "none") + newbies + theme(legend.position = "bottom") + labs(fill = "Group type") 


# We want to plot overall score per each round seperately for homo and hetero groups
ggplot(Class_03, aes(
  x = round, y = score, color = group_type)) + 
  geom_point(alpha=I(0.5)) + 
  geom_smooth(method = "lm") +
  labs(title = "Score of the two different groups per round",  
       subtitle = "Effect of teaching = 0.03") + ylab("score") +
  theme(text=element_text(size=30,  family="serif")) + 
  scale_color_manual(values = c( "forestgreen", "#66B2FF"))
  

# We want to plot the overall score for each agent_type per group
ggplot(Class_03, aes(round, score, color = group_type)) + 
  geom_point(alpha=I(0.5)) + geom_smooth(method = "lm") + facet_wrap(~agent_type)  + 
  labs(title = "Score per round for each agent type", subtitle = "Effect of teaching = 0.03" ) +  
  ylab ("score") +
  theme(text=element_text(size=30,  family="serif")) + 
  scale_color_manual(values = c( "forestgreen", "#66B2FF"))


# development in probability score
ggplot(Class_03, aes(x = round, y = solving_rate, color = agent_type)) + 
  geom_point() + facet_grid(~group_type) + 
  geom_smooth(method = "lm") +
  labs(title = "Probability of answering correct per round", subtitle = "Effect of teaching = 0.03") +
  ylab("solving rate") +
  labs(fill = "Agent type") +
  theme(text=element_text(size=16,  family="serif")) + 
  scale_color_manual(values = c( "forestgreen", "#66B2FF", "#FF6666", "#FFFF66"))

```